---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CycleInfraLnd

The goal of this CycleInfraLnd R package is to access and download data from the Transport for London Cycling Infrastructure Database into R as spatial data (Simple features).

The Cycling Infrastructure Database contains the following assets that are either lines(l) or points(p): 

* Advanced Stop Line (l)

* Crossing (l)

* Cycle lane/track (l)

* Restricted Route (l)

* Cycle Parking (p)

* Restricted Point (p)

* Signage (p)

* Signal (p)

* Traffic Calming (p)

More information on the CID can be found [here](https://data.london.gov.uk/dataset/cycling-infrastructure-database) and in this [TFL blog](https://blog.tfl.gov.uk/2019/08/13/data-drop-cycling-infrastructure-database/).

The [Database Schema](https://cycling.data.tfl.gov.uk/CyclingInfrastructure/documentation/cid_database_schema.xlsx), [Asset Information Guide](https://cycling.data.tfl.gov.uk/CyclingInfrastructure/documentation/asset_information_guide.pdf) and [README](https://cycling.data.tfl.gov.uk/CyclingInfrastructure/documentation/CIDASSETS_README.docx) provide important and useful information about the content of the database and how it was collected. 



## Installation

You can install the developed version of CycleInfraLnd from [Github](https://github.com/PublicHealthDataGeek/CycleInfraLnd) with:

``` r
# install.packages("devtools")
devtools::install_github("PublicHealthDataGeek/CycleInfraLnd")
```
## Examples

These examples show the two functions in this package that allow you to obtain either lines or points from the Cycling Infrastructure Database.  The example list in the help file contains all variations of this code for each of the different asset types i.e. the different lines and points that are available in the Cycling Infrastructure Database.  

```{r example}
library(CycleInfraLnd)

get_cid_lines(type = "advanced_stop_line")

get_cid_points(type = "signal")
```


